---
title: "kmeans"
author: "joshna katta"
date: "2022-11-06"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#loading required packages
library(flexclust)
library(cluster)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(factoextra)
```

```{r}
pharma.df = read.csv("C:/Users/Pavan Chaitanya/Downloads/Pharmaceuticals.csv")
colMeans(is.na(pharma.df))
```

```{r}
#normalizing the data 
norm.pharma = scale(pharma.df[,-c(1:2,12:14)])
```
#using wss method finding the optimal k value 
```{r}
wss = fviz_nbclust(norm.pharma,kmeans,method = "wss")
wss
```
#finding the optimal k value from the silhouette method
```{r}
silhouette = fviz_nbclust(norm.pharma,kmeans,method="silhouette")
silhouette
```

*here we got two different k values are from wss method is k= 2 and silhouette method was k = 5*
```{r}
#formulating the kmeans with wss 
wss_kmeans = kmeans(norm.pharma,centers = 2,nstart=50)
wss_kmeans
```


```{r}
silhouette_kmeans =kmeans(norm.pharma,centers = 5,nstart = 50)
silhouette_kmeans
```
*therefore by performing the wss method wet get clusters of size 11 and 10.*
*therefore by performing the silhousette method wet got 5 clusters of sizes are 8,3,2,4,4*

*cluster plot for wss*
```{r}
fviz_cluster(wss_kmeans,data = norm.pharma)


```
```{r}
fviz_cluster(silhouette_kmeans,data = norm.pharma)
```
*5 clusters have been noticed from the above. The symbols/shapes in each cluster are 'centroids' of that specific cluster.
Nstart value 25 and above is defined as no other centroid can be taken into consideration until new data is being added.*
*(b) Interpret the clusters with respect to the numerical variables used in forming the clusters.*
```{r}
#interpretation
silhouette_clusters = silhouette_kmeans$cluster
silhouette_cluster = as.data.frame(silhouette_clusters)
silhouette_2 = cbind(pharma.df,silhouette_clusters)
cluster_mean = silhouette_2 %>% group_by(silhouette_clusters) %>%
summarise_all("mean")
cluster_mean
```



#c.pattern with variables 10 to 12.
```{r}
library(hrbrthemes)
#median_recommendation vs cluster
pharma2 = pharma.df[,c(12,13,14)]
pharma3 =cbind(pharma2,silhouette_cluster)

ggplot(pharma3,aes(x=silhouette_clusters,fill= Median_Recommendation))+geom_bar(position = "dodge")+labs(title = "Median_Recommendation vs cluster",
    x ="cluster"                                                                                     ) +
  theme_bw()
```

*location versus cluster*
```{r}
ggplot(pharma3,aes(x=silhouette_clusters,fill = Location))+ geom_bar(position = "dodge")
labs(
  title = "location vs cluster",
  x= "cluster"
)+
  theme_bw()
```
*cluster versus exchange*
```{r}
ggplot(pharma3,aes(x=silhouette_clusters, fill = Exchange,))+
geom_bar(postion = "dodge")+
labs(
title ="exchange vs cluster",
x="cluster"
)+
theme_bw()

```

#D)
1.cluster 1 is "Poorly Performing Pharma", has low performance across all features and extremely high BETA and Leverage values.
2.cluster 2 "Overpriced Pharma", with a high PE ratio
3.cluster 3 "Currently Profitable Pharma," which has the lowest revenue growth but a solid net profit margin.
4."Big Pharma" is in Cluster 4, and it has high market capitalization, ROE, ROA, asset turnover, and net profit margin.
5.The Sil Cluster 5 with the highest Rev Growth is "Future Potential Pharma."